Untitled

### 2023-08-19 code/analysis_Redo.Rmd
added in the geographic analysis

df.sum <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
  ungroup() %>% 
  #rename(`Grant Number` = Grant.Number, `Surplus as a pct of before dep expenses` = Surplus.as.a.pct.of.after.dep.expenses) %>% 
  #filter(MarketShare < 0.4) %>%  #median(MarketShare, na.rm = TRUE) - 0.25
  #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 15000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 1.75 or 7.75
  select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Total, IMM2yo:DepScrn) %>%
  # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
  #                                           mutate(ZipFilter = ifelse(Total < 12000, 1,
  #                                                              ifelse(Total > 12000, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
  inner_join(df.qual.exp %>% filter(Year == 2016) %>% #mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% 
               select(`Grant Number`, ZipFilter, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("Grant Number")) %>% 
  select(`Grant Number`, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Pct.NHA:Pct.Children, MCD, COM, MCR, Total, IMM2yo:DepScrn) %>% 
  mutate(Tx = ifelse(Year >= Att & Att > 0, 1, 0)) %>% 
  unique() %>% 
  mutate(NewQuality = (CRC + ChildBMI + AdultBMI + Tobac + DepScrn) / 5)

#library(did2s)

did2s(
      data = df.sum %>% inner_join(df.qual.exp %>% filter(MarketShare > 1) %>% select(`Grant Number`) %>% unique(), by = c("Grant Number")), 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

#select(ID, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z) %>% left_join(df.qual.exp %>% select(ID, Year, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("ID","Year"))
out.qual <- event_study(data = df.qual.exp %>% filter(ZipFilter == 1), 
  yname = "Altmans.Z", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM)

out.qual %>% 
  filter(estimator %notin% c("Borusyak, Jaravel, Spiess (2021)")) %>% 
filter(abs(term) <= 3) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)

## Variations

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) %>% 
  filter(Year %in% c(2015, 2019)) %>% 
  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
  mutate(ds = `2019` - `2015`) %>% 
    ungroup() %>% 
    mutate(filt = ifelse(ds > median(ds, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(ds < 1),#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) , by = c("Grant Number","Year")) ,#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(avgdist / 10) + I(Tx *as.numeric(avgdist / 10)),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% left_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% filter(is.na(DistToClosestSite) | DistToClosestSite > 5),
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) ,
        cluster_var = "ID",
      verbose = FALSE
    )

set.seed(345)
did2s(
      data = df.sum %>% left_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% 
        group_by(ID) %>% 
  mutate(DistToClosestSite = ifelse(is.na(DistToClosestSite), sample(size = 1, df.z.dist$DistToClosestSite, replace = T), DistToClosestSite)),
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(DistToClosestSite / 1) + I(Tx *as.numeric(DistToClosestSite / 1)),
        cluster_var = "ID",
      verbose = FALSE
    )

@@

## Rival selecting where to put new site

@@

event_study(data = dfc.new %>% left_join(dfc %>% select(ID, Year, Pct.NHA:Pct.COM), by = c("ID","Year")) %>% 
              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/Assets < 0.05)# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                   %>% select(ID) %>% unique() , by = c("ID")), 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>% 
  filter(abs(term) <= 5) %>% 
  #filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)

@@

>>>>

@@

## OTher splits

@@

event_study(data = dfc.new %>% left_join(dfc %>% select(ID, Year, Pct.NHA:Pct.COM), by = c("ID","Year")) %>% 
              inner_join(dfc %>% filter(Year == 2010 )# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                   %>% select(ID) %>% unique() , by = c("ID")), 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>% 
  filter(abs(term) <= 5) %>% 
  #filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)

@@

## Treatment vs control, only in zip code of interest
df.z <- left_join(dfc #%>% filter(`Grant Number` != "H80CS00225")
                  , #uds.zip %>% mutate(Zip = `Zip Code`) %>% select(`Grant Number`, Zip) %>% unique() , by = c("Grant Number")) %>%
                  uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
                    filter(Year %in% c(2010:2021)) %>% 
              select(`BHCMIS ID`, Zip) %>%
              unique() %>% filter(!is.na(Zip)), by = c("BHCMIS ID")) %>%
  left_join(uds.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear", "Zip" = "ZipCode")) %>%
  filter(!is.na(GrantNumber)) %>% 
  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
         ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z) %>%
  arrange(`BHCMIS ID`, Zip, Year) %>% 
  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)

df.z <- df.z %>%
  left_join(df.z %>%
            filter(Tx.z == 1) %>%
            group_by(ID, Zip) %>%
            summarise(Att.z = min(Year)), by = c("ID", "Zip")) %>%
  mutate(Att.z = ifelse(is.na(Att.z), 0, Att.z)) #%>%
# inner_join(df.z %>% filter(!is.na(Clinics)) %>% group_by(ID) %>% summarise(n()) %>% filter(`n()` == length(unique(df.qual.exp$Year))), by = c("ID")) #%>% filter(Att == Att.z)

## Whole zip as one measure

df.z.full <- df.z %>% ############## NOTE: Original +500 effect was recoved with Att.z, not Att
  select(Zip, Att.z, Year) %>% 
  unique() %>% 
  left_join(uds.zip, by = c("Zip" = "ZipCode", "Year" = "ReportingYear")) %>% 
  left_join(dfc %>% 
            select(`BHCMIS ID`, Year, Qcomp), by = c("BHCMISID" = "BHCMIS ID", "Year")) %>% 
  group_by(Zip, Year, Att.z) %>% 
  summarise(
    Total.z = sum(NumberofPatients, na.rm = TRUE), 
    Quality.z = sum(NumberofPatients * Qcomp, na.rm = TRUE) / Total.z) %>% 
  ungroup() %>% 
  mutate(ID = as.numeric(as.factor(Zip)))# %>% group_by(`Grant Number`, Year, Att) %>% summarise(ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE)) # %>% filter(Year > 2015),

df.zip.1 <- df.z %>% select(ID, Year, Att, NumberofPatients)
df.zip.2 <- df.z.full %>% select(ID, Year, Att.z, Total.z:Quality.z)

## DIstance Rival Traveled
```{r}

## Distance of Competitor to New Site
df.z.dist <- df.z.full %>% 
  filter(Att.z == Year) %>% 
  select(Zip:Total.z) %>% 
  left_join(uds.sites.full %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
  left_join(df.z %>% filter(Tx == 1) %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
  filter(`BHCMIS ID.x` != `BHCMIS ID.y`)

## Read in Centroid Data
zip.centroids <- read.csv("/Users/jhm65/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
  select(ZipCode, X, Y)
## Add missing centroids
zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
                                      c(ZipCode = "95951", X = -121.98, Y = 39.73), 
                                      c(ZipCode = "99733", X = -144.166941, Y = 65.799773)) %>% 
  mutate(X = as.numeric(X), Y = as.numeric(Y))

df.z.dist <- df.z.dist %>% mutate(DistToClosestSite = NA, ZipOfClosestSite = NA)

for (g in 1:nrow(df.z.dist)){
#g <- 1
 temp <- rbind(zip.centroids %>% filter(ZipCode == df.z.dist[g,]$Zip), 
          zip.centroids %>% filter(ZipCode %in% unique(uds.sites.full[uds.sites.full$`BHCMIS ID` == df.z.dist[g,]$`BHCMIS ID.x` & uds.sites.full$Year == df.z.dist[g,]$Year,]$Zip))) %>% 
   unique()
  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean"))[-1,1]
  df.z.dist[g,]$DistToClosestSite <-  min(mm) * 111.139
  df.z.dist[g,]$ZipOfClosestSite  <- ifelse(is.na(temp[2,]$ZipCode), temp[1,]$ZipCode, unlist(temp[-1,]$ZipCode[rank(mm) == 1]))
}

#df.z.dist[19,]$DistToClosestSite <- 0
df.z.dist <- df.z.dist %>% 
  filter(!is.infinite(DistToClosestSite))

df.z.dist <- df.z.dist %>% 
  inner_join(df.z.dist %>% group_by(`BHCMIS ID.y`) %>% summarise(Att.z = min(Att.z)), by = c("BHCMIS ID.y", "Att.z")) %>% 
  unique()

mean(df.z.dist$DistToClosestSite)
quantile(df.z.dist$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))

# mean(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite)
# mean(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite)
# 
# quantile(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
# quantile(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))

zipsize <- zctas(starts_with = c(df.z.dist$Zip, df.z.dist$ZipOfClosestSite), year = 2010)

## Original Figure
df.z.dist.plot <- df.z.dist %>% 
  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  left_join(uds.sites.full %>% select(Zip, `Site State`) %>% unique(), by = c("Zip")) %>% 
  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  arrange(desc(DistToClosestSite)) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
  mutate(Density.NewZip = TotalPop / Area.SQmiles, 
         l.density = log(TotalPop / Area.SQmiles)) %>% 
  unique()

df.z.dist.plot %>% 
  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite)) + geom_point(aes(size = Area.SQmiles)) +
  ggtitle("Distance from Rival's newly competing zip ocde to closest incumbent zip code by Density and Area of newly competing zip code")

summary(lm(DistToClosestSite ~ log(Density.NewZip), data = df.z.dist.plot))

# Updated Figure
df.z.dist.plot <- df.z.dist.plot %>% 
  select(Zip:ZipOfClosestSite, Density.NewZip) %>% 
  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("ZipOfClosestSite" = "GEOID10")) %>% 
  left_join(uds.sites.full %>% select(Zip, `Site State`) %>% unique(), by = c("ZipOfClosestSite" = "Zip")) %>% 
  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "ZipOfClosestSite" = "ZipCode")) %>% 
  arrange(desc(DistToClosestSite)) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
  mutate(Density.Origin = TotalPop / Area.SQmiles)

df.z.dist.plot %>% 
  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite, color = log(Density.Origin))) + geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10))+ theme_minimal()+
  ylab("Distance from Competative to closest Rival Site (km)") +
  ggtitle("Distance from newly competative Zip to Rival's closest existing zip, by log Density of areas")

p <- df.z.dist.plot %>% 
  ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
  geom_point(aes(size = DistToClosestSite, colour = DistToClosestSite)) + 
  scale_colour_gradientn(colours = c("green","lightblue","purple"),
                         values = c(1.0,0.7,0.1,0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
  theme_minimal() + ylab("Log Population Density of New Zip Code") + 
  xlab("Log Population Density of Nearest Service Area Zip Code") + 
  labs(color = "Distance Travelled to\nOpenNew Site (km)") + 
  guides(size = FALSE) + xlim(0.5, 11.5) + ylim(0.5, 11.5)
p

summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))
```

## Primary effects by distance rival travelled
```{r}
set.seed(123)
df.dist <- df.core %>% 
  left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Dist.random = sample(size = 1, unique(df.z.dist.plot$DistToClosestSite), replace = TRUE), 
         Dist.random = ifelse(Att > 0, DistToClosestSite, Dist.random))

#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.5), na.rm = TRUE)

splits1 <- c(min(df.dist$Dist.random, na.rm = TRUE)-1, splits)
splits2 <- c(splits, max(df.dist$Dist.random, na.rm = TRUE))

did.dist <- c(0, 0, 0, 0)
for (g in 1:(length(splits) + 1)){
  for (j in 10:12){

  df.temp <- df.dist[,c(1:9, j, 13:ncol(df.dist))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(Dist.random > splits1[g] & Dist.random <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

  did.dist <- rbind(did.dist, outcomes$coeftable)

did.dist <- did.dist[-1,]
rownames(did.dist) <- NULL

data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.dist[,1]), 
      SD = as.numeric(did.dist[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by Baseline Size")
```

## Rival selecting where to put new site, takes 30+ minutes to work

## Build the first part of the dataset

df.spill <- df.z %>% 
  left_join(df.z.dist %>% 
  select(`BHCMIS ID.y`, Zip) %>% 
    unique() %>% 
    rename(ZipOfComp = Zip), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
  #filter(!is.na(ZipOfComp)) %>% 
  #mutate(ZipOfComp = ifelse(`BHCMIS ID` == "H80CS00765", 95991, ZipOfComp)) %>% 
  left_join(zip.centroids, by = c("Zip" = "ZipCode")) %>% 
  left_join(zip.centroids, by = c("ZipOfComp" = "ZipCode")) %>% 
  mutate(Dist = sqrt((X.x - X.y) ^ 2 + (Y.x - Y.y) ^ 2) * 111.139) %>% 
  mutate(Dist.f = ifelse(is.na(Dist), "-1",
                  ifelse(Dist == 0, 0, 
                  ifelse(Dist > 0 & Dist < 20, 1, 
                  ifelse(Dist >= 20 & Dist < 50, 2, 
                  ifelse(Dist >= 50 & Dist < 100, 3, 4)))))) %>% 
  #filter(is.na(Dist.f) | Dist.f == 2) %>% 
  left_join(uds.sites.full %>% 
              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`BHCMIS ID`, Year, Zip) %>% 
              summarise(Sites = n(), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)), by = c("BHCMIS ID","Year", "Zip")) %>% 
  mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar))

dist.vecs <- df.spill[!is.na(df.spill$Dist),]$Dist

df.spill %>% 
  group_by(Dist.f) %>% 
  summarise(n())

## Find neighbors based on some circle around FQHC zip

mm <- dist(zip.centroids[,2:3])
mm <- as.matrix(mm) * 111.139

mm.2 <- mm[zip.centroids$ZipCode %in% unique(df.spill$Zip),]

mm.2 <- as.matrix((mm.2 < 50) + 0 )
rowSums(mm.2)

mm.3 <- c(CenterZip = 0, Year = 0, Competing.Sites = 0)
for (g in 1:dim(mm.2)[1]){
  mm.3 <- rbind(mm.3, cbind(CenterZip = zip.centroids[rownames(mm.2)[g],]$ZipCode, zip.centroids[names(mm.2[g,][which(as.vector(mm.2[g,] == 1))]),]) %>% 
  left_join(uds.sites.full %>% filter(Year %in% c(2010:2021)) %>% group_by(Year, Zip) %>% summarise(Sites.Total = n()), by = c("ZipCode" = "Zip")) %>% 
  left_join(df.spill %>% select(`BHCMIS ID`, Year, Zip, Sites), by = c("ZipCode" = "Zip", "Year")) %>% 
  mutate(Sites.Total = ifelse(is.na(Sites.Total), 0, Sites.Total), 
         Sites = ifelse(is.na(Sites), 0, Sites), 
         Competing.Sites = Sites.Total - Sites) %>% 
  filter(CenterZip != ZipCode) %>% 
  group_by(CenterZip, Year) %>% 
  summarise(Competing.Sites = sum(Competing.Sites)) %>% 
    as.matrix())
}

mm.3 <- mm.3[-1,]

#mm.100 <- mm.3 %>% data.frame() 
#mm.60 <- mm.3 %>% data.frame() 
#mm.50 <- mm.3 %>% data.frame() 
#mm.20 <- mm.3 %>% data.frame() 
#mm.10 <- mm.3 %>% data.frame()

#mm.3 <- mm.50

## NumberofPatients and Total.Hours are the best cases, controlling for Sites
```{r}

 i <- 10
  df.temp <- df.spill2[,c(1:5, 11, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]

for (i in 12:15){
  df.temp <- df.spill2[,c(1:5, 11, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
}

  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total"),   TEs, TEs_Dist)
```

df.spill2 <- df.spill %>% 
  left_join(mm.3 %>% data.frame() %>% mutate(Year = as.numeric(Year)), by = c("Zip" = "CenterZip","Year")) %>% 
  mutate(Competing.Sites = as.numeric(ifelse(is.na(Competing.Sites), 0, Competing.Sites)), 
         D = ifelse(Competing.Sites > 0, 1, 0))

#length(unique(df.spill2[is.na(df.spill2$Dist),]$Zip))  #1893 or 1893 * 5

set.seed(234)  #232
df.spill2 <- df.spill2 %>% 
  group_by(Zip) %>% 
  mutate(Dist = ifelse(is.na(Dist), sample(dist.vecs, 1, replace = T), Dist), 
                                  Att.viz = ifelse(Att == 0, rep(sample(c(2012:2021), 1, replace = T), each = 1), Att)) %>% 
  mutate(Dist.rounded = as.factor(ceiling(Dist / 10)))

df.spill2 <- df.spill2 %>% 
  ungroup() %>% 
  #filter(MarketShare < median(MarketShare, na.rm = TRUE)) %>% 
  select(`BHCMIS ID`, Tx, D, Att, Att.viz, Dist, Dist.rounded, Year, Zip, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients) %>%
  #inner_join(df.qual.exp %>% filter(Year == 2012) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`BHCMIS ID`, ZipFilter), by = c("BHCMIS ID")) %>% 
    select(Tx, D, Dist, Year, Zip, `BHCMIS ID`, Att, Att.viz, Dist.rounded, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients) # %>% filter(ZipFilter == 2)

  i <- 10
  df.temp <- df.spill2[,c(1:5, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]

for (i in 11:15){
  df.temp <- df.spill2[,c(1:5, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
}

p.spill <- df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
  filter(Att > 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), NumberofPatients = mean(NumberofPatients, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, Total.Hours)) %>% 
  mutate(Sites = Sites_1 - Sites_0, 
         NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
         Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
  left_join(df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
  filter(Att == 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), NumberofPatients = mean(NumberofPatients, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, Total.Hours, Total.Hours)) %>% 
  mutate(Sites.control = Sites_1 - Sites_0, 
         NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
         Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
    select(Dist.rounded, Sites.control:Total.Hours.control), by = c("Dist.rounded")) %>% 
  mutate( Locations = Sites - Sites.control, 
         `Patients` = NumberofPatients - NumberofPatients.control, 
         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
  mutate(`Treated Zips` = Counts_0 / 3) %>% 
  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
  ggtitle("Figure 4 - Unadjusted DID Estimates by Distance to Competitive Zip")

suppressWarnings(print(p.spill))

output <- cbind(TEs %>% 
  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
    select(Estimate,`95% LB`, `95% UB`) ,
